Surrogate Regret Bounds for Polyhedral Losses

### 2021-05-28 rates-neurips-21/rates.tex
more refs

Some references by setting.  P = polyhedral.  Surrogate regret bound: L = linear, Q = quadratic (sqrt).  LB = gives a ``lower bound'' for the surrogate regret too.
\begin{itemize}
\item Binary classification.
  \begin{itemize}
  \item \citet{zhang2004statistical} -- early analysis, didn't use ``surrogate'' but had some quantitative bounds that implied consistency
  \item \citet{bartlett2006convexity} -- some bounds for margin losses
  \item \citet{reid2009surrogate} -- tight (?) bounds for general proper composite losses
  \item \citet{mahdavi2014binary} -- consider the generalization rate of the surrogate together with the ``excess risk bound'' (surrogate regret bound) (\textbf{and} the optimization actually), both as a function of the smoothness parameter of the surrogate.  They don't seem to give lower bounds on the excess risk bound though, just a degrading upper bound on it.  Still, very close to our work (and more generally the ``full stack'' idea!) in spirit.
  \end{itemize}

@@

\item Abstain
  \begin{itemize}
  \item[P,L] \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all \textbf{linear}, each ``from scratch''.
  \item[Q] \citet{yuan2010classification} -- Smooth? losses and characterizations for abstain; \textbf{binary classification only}
  \item[P,L] \citet{bartlett2008classification} -- The OG abstain paper, with a polyhedral hinge-like loss.  \textbf{Linear} regret bound.
  \end{itemize}

@@

\item Structured prediction (covering lots of target problems simultaneously)
  \begin{itemize}
  \item[Q,LB] \citet[Theorem 7]{osokin2017structured} -- Prove excess risk bounds for a broad family of structured prediction problems, using a specific quadratic surrogate.  Also give an upper bound on the calibration function, i.e. a lower bound in the sense that we prove (Theorem 8).
  \item[Q] \citet{ciliberto2016consistent} -- Calibration function for a similar quadratic surrogate, for a similarly general class of structed pred problems.
  \item[Q,LB] \citet[Theorem 4.4]{nowak2019general} -- Even more general than the previous Bach paper \cite{osokin2017structured} (e.g. includes ordinal regression).  Quadratic risk bound for a proper loss for the mean from a strongly-convex potential/entropy.
    Also give a matching lower bound in our sense (Theorem 4.5).
  \item[Q] \citet[Proposition 5]{blondel2019structured} -- Tighter losses, still quadratic, still quadratic excess risk.
  \end{itemize}

@@

\item Fast rates
  \begin{itemize}
  \item \citet{koren2015fast} -- fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) .  Note here exp-concavex is in the \emph{parameter}.  So $F(\theta) = L(h_\theta(x),y)$ should be exp-concave in $\theta$.  For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
  \item Tim et al paper than Anish referenced!
  \end{itemize}

@@

%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
\raft{Maybe a good place to cite the IEEE rates paper}
While much is known about surrogate regret bounds for particular problems, such as binary classification and bipartite ranking, general results which span multiple target problems are sparse.
Lacking such results, authors instead often prove bounds for specific surrogate losses from scratch, e.g. \raf{abstain, others?}.
\bo{Furthermore, to this point, linear transfer guarantees have been relatively rare in the literature? True?}

>>>>

Some references by setting.  P = polyhedral.  Surrogate regret bound: L = linear, Q = quadratic (sqrt).  $\leq$ = gives a ``lower bound'' for the surrogate regret too.
\begin{itemize}
\item Binary classification.
  \begin{itemize}
  \item \citet{zhang2004statistical} -- early analysis, didn't use ``surrogate'' but had some quantitative bounds that implied consistency
  \item \citet{bartlett2006convexity} -- tight bounds for \textbf{all margin losses}
  \item \citet{reid2009surrogate} -- tight bounds for \textbf{all proper composite losses}
  \item \citet{mahdavi2014binary} -- consider the generalization rate of the surrogate together with the ``excess risk bound'' (surrogate regret bound) (\textbf{and} the optimization actually), both as a function of the smoothness parameter of the surrogate.  They don't seem to give lower bounds on the excess risk bound though, just a degrading upper bound on it.  Still, very close to our work (and more generally the ``full stack'' idea!) in spirit.
  \end{itemize}

@@

\item Abstain and hierarchical
  \begin{itemize}
  \item[P,L] \citet{ramaswamy2018consistent} -- Abstain paper; shows bounds for 3 different surrogates, all \textbf{linear}, each ``from scratch''.
  \item[Q] \citet{yuan2010classification} -- Smooth? losses and characterizations for abstain; \textbf{binary classification only}
  \item[P,L] \citet{bartlett2008classification} -- The OG abstain paper, with a polyhedral hinge-like loss.  \textbf{Linear} regret bound.
  \item[P,L] \citet{ramaswamy2015hierarchical} -- Nested OvA surrogate; linear bound
  \end{itemize}

@@

\item Structured prediction (covering lots of target problems simultaneously)
  \begin{itemize}
  \item[Q,$\leq$] \citet[Theorem 7]{osokin2017structured} -- Prove excess risk bounds for a broad family of structured prediction problems, using a specific quadratic surrogate.  Also give an upper bound on the calibration function, i.e. a lower bound in the sense that we prove (Theorem 8).
  \item[Q] \citet{ciliberto2016consistent} -- Calibration function for a similar quadratic surrogate, for a similarly general class of structed pred problems.
  \item[Q,$\leq$] \citet[Theorem 4.4]{nowak2019general} -- Even more general than the previous Bach paper \cite{osokin2017structured} (e.g. includes ordinal regression).  Quadratic risk bound for a proper loss for the mean from a strongly-convex potential/entropy.
    Also give a matching lower bound in our sense (Theorem 4.5).
  \item[Q] \citet[Proposition 5]{blondel2019structured} -- Tighter losses, still quadratic, still quadratic excess risk.
  \end{itemize}

@@

\item Fast rates
  \begin{itemize}
  \item \citet{koren2015fast} -- fast rates for exp-concave surrogates ($O(d/n)$ where $d$ is the dimension) .  Note here exp-concavex is in the \emph{parameter}.  So $F(\theta) = L(h_\theta(x),y)$ should be exp-concave in $\theta$.  For $\alpha>0$ we say $f$ is $\alpha$-exp-concave if $x \mapsto \exp(-\alpha f(x))$ is concave.
  \item \citet{grunwald2015fast} -- Tim et al paper than Anish referenced!  
  \end{itemize}

@@

%As the above example illustrates, understanding the behavior of $\zeta$ near $0$ is crucial to analyzing the overall generalization rate; were $\zeta$ linear near $0$, the overall rate would have been a fast $O(1/n)$.
\raft{Maybe a good place to cite the IEEE rates paper}
While much is known about surrogate regret bounds for particular problems, such as binary classification~\citep{zhang2004statistical,bartlett2006convexity,reid2009surrogate,mahdavi2014binary}

and bipartite ranking, general results which span multiple target problems are sparse.
Lacking such results, authors instead often prove bounds for specific surrogate losses from scratch, e.g. \raf{abstain, others?}.
\bo{Furthermore, to this point, linear transfer guarantees have been relatively rare in the literature? True?}
